01 - TreehopperFitness: Quality control

### 2023-08-23 scripts/Publilia-01-qc.Rmd
update manual check csv writing to use `here()` and new dir structure. Resolves https://github.com/micahpf/PubliliaFitness/issues/4#issue-1864036908

# checking number of ambiguous entries that need to be resolved
nymph_text_conflict_data <- All_data_v4 %>% # nymph_text_conflict: 10 on 2019/09/24; 0 on 2019/09/26
  left_join(N1_status, by = c("Date", "location", "N1")) %>%
  left_join(N2_status, by = c("Date", "location", "N2")) %>%
  left_join(N5_status, by = c("Date", "location", "N5")) %>%
  group_by(row_number()) %>% 
    filter(any(c(N1_text_conflict, N2_text_conflict, N5_text_conflict))) %>%
  ungroup() %>%
  select(Date, Dorm, Plant, Leaf, Female_ID, Eggs, N1, N2, N5, nymph_origin, Notes, N1_text_conflict, N2_text_conflict, N5_text_conflict)
# write_csv(egg_text_conflict_data, "egg_text_conflict_data.csv")

nymph_status_missing_data <- All_data_v4 %>% # nymph_status_missing: 17 on 2019/09/24; 5 on 2019/09/26 (all ok to ignore)
  left_join(N1_status, by = c("Date", "location", "N1")) %>%
  left_join(N2_status, by = c("Date", "location", "N2")) %>%
  left_join(N5_status, by = c("Date", "location", "N5")) %>%
  group_by(row_number()) %>% 
  filter(any(c(N1_status_missing, N2_status_missing, N5_status_missing))) %>%
  ungroup() %>%
  select(Date, Dorm, Plant, Leaf, Female_ID, Eggs, N1, N2, N5, nymph_origin, Notes, N1_status_missing, N2_status_missing, N5_status_missing)
# write_csv(egg_status_missing_data, "egg_status_missing_data.csv")

@@

## 2.9 - Manually check hatch dates using the "not hatched" notes from field using `check_hatch_date` sheet
Use the "not hatched" notes (from original field notes; typically b/c nymphs present but they are immigrants, not hatched from the focal clutch) to inform first pass of hatch date revisions
Again these changes were specified in the `check_hatch_date` sheet and are applied here without changing the original data file.
```{r}
# Create `check_hatch_date` sheet for checking "not hatched" notes and suggesting manual revisions
check_hatch_date <- All_data_v4  %>%
  filter(grepl("not", Notes, ignore.case = TRUE), grepl("hatch", Notes, ignore.case = TRUE)) %>%
  distinct(location)
# write_csv(check_hatch_date, "check_hatch_date_tmp.csv")
```

@@

# write_csv(ant_text_conflict, "ant_text_conflict.csv") # resolved 2019-10-08
```

@@

# write_csv(short_unhatched_days_check, "short_unhatched_days_check_tmp.csv")

@@

# write_csv(never_hatched_check, "never_hatched_check_tmp.csv")

# write_csv(clutch_status_stats_v1, "egg_measures_check_tmp.csv")
```

@@

# write_csv(NOr_manual_check_table %>% filter(revise_NOr == "MANUAL CHECK"), "NOr_manual_check_tmp.csv")

>>>>

# checking number of ambiguous entries that need to be resolved
nymph_text_conflict_data <- All_data_v4 %>% # nymph_text_conflict: 10 on 2019/09/24; 0 on 2019/09/26
  left_join(N1_status, by = c("Date", "location", "N1")) %>%
  left_join(N2_status, by = c("Date", "location", "N2")) %>%
  left_join(N5_status, by = c("Date", "location", "N5")) %>%
  group_by(row_number()) %>% 
    filter(any(c(N1_text_conflict, N2_text_conflict, N5_text_conflict))) %>%
  ungroup() %>%
  select(Date, Dorm, Plant, Leaf, Female_ID, Eggs, N1, N2, N5, nymph_origin, Notes, N1_text_conflict, N2_text_conflict, N5_text_conflict)
# write_csv(egg_text_conflict_data, here("data/manual_check/egg_text_conflict_data.csv"))

nymph_status_missing_data <- All_data_v4 %>% # nymph_status_missing: 17 on 2019/09/24; 5 on 2019/09/26 (all ok to ignore)
  left_join(N1_status, by = c("Date", "location", "N1")) %>%
  left_join(N2_status, by = c("Date", "location", "N2")) %>%
  left_join(N5_status, by = c("Date", "location", "N5")) %>%
  group_by(row_number()) %>% 
  filter(any(c(N1_status_missing, N2_status_missing, N5_status_missing))) %>%
  ungroup() %>%
  select(Date, Dorm, Plant, Leaf, Female_ID, Eggs, N1, N2, N5, nymph_origin, Notes, N1_status_missing, N2_status_missing, N5_status_missing)
# write_csv(egg_status_missing_data, here("data/manual_check/egg_status_missing_data.csv")

@@

## 2.9 - Manually check hatch dates using the "not hatched" notes from field using `check_hatch_date` sheet
Use the "not hatched" notes (from original field notes; typically b/c nymphs present but they are immigrants, not hatched from the focal clutch) to inform first pass of hatch date revisions
Again these changes were specified in the `check_hatch_date` sheet and are applied here without changing the original data file.
```{r}
# Create `check_hatch_date` sheet for checking "not hatched" notes and suggesting manual revisions
check_hatch_date <- All_data_v4  %>%
  filter(grepl("not", Notes, ignore.case = TRUE), grepl("hatch", Notes, ignore.case = TRUE)) %>%
  distinct(location)
# write_csv(check_hatch_date, here("data/manual_check/check_hatch_date_tmp.csv")
```

@@

# write_csv(ant_text_conflict, here("data/manual_check/ant_text_conflict.csv") # resolved 2019-10-08
```

@@

# write_csv(short_unhatched_days_check, here("data/manual_check/short_unhatched_days_check_tmp.csv")

@@

# write_csv(never_hatched_check, here("data/manual_check/never_hatched_check_tmp.csv")

# write_csv(clutch_status_stats_v1, here("data/manual_check/egg_measures_check_tmp.csv")
```

@@

# write_csv(NOr_manual_check_table %>% filter(revise_NOr == "MANUAL CHECK"), here("data/manual_check/NOr_manual_check_tmp.csv")
